Fail Faster

### 2025-03-23 paper/paper.tex
blah

\subsubsection{Do staged type-derived generators reduce timeouts?}
In addition to \camlname's overall bug-finding speed, we evaluate 
the performance of its type-derived generators---specifically, 
whether they can transform previously intractable tasks into 
tractable ones. Out of 78 tasks that initially timed out, 
50 (64\%) completed successfully after our interventions. 
This suggests that staged type-derived generators can provide 
significant performance improvements for free---that is, without 
requiring any additional effort from the user.
\section{Beyond Strict Functional Languages}
\label{section:other-langs}

>>>>

\subsubsection{Do staged type-derived generators reduce timeouts?}
In addition to \camlname's overall bug-finding speed, we evaluate 
the performance of its type-derived generators---specifically, 
whether they can transform previously intractable tasks into 
tractable ones. Out of 78 tasks that initially timed out, 
50 (64\%) completed successfully after our interventions. 
This suggests that staged type-derived generators can provide 
significant performance improvements for free---that is, without
 any additional effort from the user.
\section{Beyond Strict Functional Languages}
\label{section:other-langs}
